---
title: "French Monuments"
author: "Genevieve Frenot"
date: "June 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## Data Source
For this Leaflet exercise we will use the list of french monuments
from the French Governement Data file
https://www.data.gouv.fr/en/datasets/r/c96fbd8f-c3c5-4c77-9a07-ea924d3298ac

We downloaded this ods file and savec it as csv manually

## Loading the data

Load the list of french monuments, assuming the original ods file has been savec as csv in the working directory

```{r read}
list <- read.csv2("french_monuments.csv", sep = ",")
```
## Adjsuting the data

Change the GPS Coordinates column names to "lon" and "lat" for Leaflet
and transform the factors to numeric values
```{r adjsut}
names(list)[names(list)=="monument_lat"] <- "lat"
names(list)[names(list)=="monument_lon"] <- "lng"
list$lat <- as.numeric(as.character(list$lat))
list$lng <- as.numeric(as.character(list$lng))

```

## Displaying the map

```{r display}
list %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=list$monument_nom)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
